### 2020-10-17 doc/manuscript/Dow_manuscript.Rmd
small changes

#Figure numbers
schematic=1 #Based on D'Orangeville Figure 1
growth_pheno_by_xylem = 2  #if we include more sites, we'll make this multi-panel
rel_growth = "2a" #Based on D'Orangeville Figure 3.a), but with relative growth
cum_growth = "2b" #Similar to D'Orangeville Figure 4.a), but with cumulative relative growth
climwin = 3
pheno_Tsensitivity = 4

@@

>>>>

#Figure numbers
schematic=1 #Based on D'Orangeville Figure 1
growth_pheno_by_xylem = 2  #if we include more sites, we'll make this multi-panel
rel_growth = "2a" #Based on D'Orangeville Figure 3.a), but with relative growth
cum_growth = "2b" #Similar to D'Orangeville Figure 4.a), but with cumulative relative growth
climwin = 3
pheno_Tsensitivity = 4
model_summary = 5

@@

model_summary_caption <- "Figure 5. (PLACEHOLDER FOR FIGURE WE DISCUSSED AT LAB MEETING)"
